Solving an optimization problem employing restraint programming

### 2015-12-13 proj2/doc/article.tex
report almost done

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage[utf8]{inputenc}
%
\begin{document}

\tableofcontents
%
\mainmatter              % start of the contributions
%
\title{Solving an optimization problem employing restraint programming}
%
\titlerunning{Restraint Programming}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{João Cabral\inst{1} \and João Mota\inst{2}}
%
\authorrunning{João Cabral \and João Mota} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{João Cabral, João Mota}
%
\institute{Faculdade de Engenharia da Universidade do Porto, Porto, Rua Roberto Frias s/n 4200-465, Portugal,\\
\email{(up201303462, up201304395)@fe.up.pt}}

@@

\keywords{optimization, restraint programming, PROLOG}
\end{abstract}
%
\section{Introduction}
Within the context of the Logic Programming course of MIEIC, the authors of this paper were asked to solve an optimization problem in the most efficient way possible using the restraint programming capabilities of SICStus PROLOG. The optimization problem under study is that of producing a working schedule for a language school that maximizes it's (monetary) gains,  given a number of inputs of variable length, aswell as a number of restrictions of various types. The rest of the paper is structured as follows:

@@

 \section{Solution Presentation}
 After the labeling phase, the solution is presented in a way that isn't easily legible by users who have no knowledge of the program's implementation. To aid in the observation and interpretation of the solution, the authors created a predicate which converts it to a more understandable format.

>>>>

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage[utf8]{inputenc}
%
\begin{document}
\tableofcontents
%
%\mainmatter              % start of the contributions
%
\title{Solving an optimization problem employing restraint programming}
%
\titlerunning{Restraint Programming}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{João Cabral\inst{1} \and João Mota\inst{2}}
%
\authorrunning{João Cabral \and João Mota} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{João Cabral, João Mota}
%
\institute{Faculdade de Engenharia da Universidade do Porto, Porto, Rua Roberto Frias s/n 4200-465, Portugal,\\
\email{(up201303462, up201304395)@fe.up.pt}}

@@

\keywords{optimization, restraint programming, PROLOG}
\end{abstract}
%
ISTO TA A FICAR APERTADO D PAGS, SE EXCEDER TIRA-SE OS VERBATIMS TODOS E OS PROFS PODEM IR LER AOS ANEXOS Q SE FODEM
\section{Introduction}
Within the context of the Logic Programming course of MIEIC, the authors of this paper were asked to solve an optimization problem in the most efficient way possible using the restraint programming capabilities of SICStus PROLOG. The optimization problem under study is that of producing a working schedule for a language school that maximizes it's (monetary) gains,  given a number of inputs of variable length, aswell as a number of restrictions of various types. The rest of the paper is structured as follows:

@@

 \section{Solution Presentation}
 After the labeling phase, the solution is presented in a way that isn't easily legible by users who have no knowledge of the program's implementation. To aid in the observation and interpretation of the solution, the authors created a predicate which converts it to a more understandable format.  Here's an example of a possible solution:

 \begin{verbatim}
 Language 0 Time Table
 _______________
Language 1 Time Table
_______________
Language 2 Time Table
_______________
Language 3 Time Table
_______________
Monday - 2 hours with professor 0
Tuesday - 2 hours with professor 0

Language 4 Time Table
_______________
Wednesday - 2 hours with professor 4
Friday - 2 hours with professor 0

Language 5 Time Table
_______________
Thursday - 2 hours with professor 3

O lucro total obtido e de 994
Resumptions: 967755
Entailments: 124262
Prunings: 348556
Backtracks: 1566
Constraints created: 749
O resultado foi obtido em 0.140 segundos.
 \end{verbatim}

 As can be seen above, a time table is created for each language in which only the days in which the class is taught are displayed, along with the number of hours taught that day and the teacher who teaches them. This is achieved via the creation of 5 predictes that make the connection between the index of days and the actual day, coupled with predicates that format and write the information on the screen. (This code that does this can be viewed in the annex, namely in the predicate printSolution).

 \section{Results}
 %BOTA GRAFICOS E TAL

 \section{Conclusions and Future Work}
 Having implemented a solution to the problem under study, the paper's authors are able to appreciate the advantages of employing restraint programming in the solving of problems that are similar to the one studied here. Indeed, the implemented solution shows that the use of this technology allows for a relatively simple implementation of a solution, when compared to possible implementations using other technologies.
%aspetos a melhorar???
